%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
\definecolor{darktext}{HTML}{000000}
\definecolor{text}{HTML}{000000}
\definecolor{graytext}{HTML}{000000}
\definecolor{lighttext}{HTML}{000000}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{profile.png}
\name{Christopher}{Goh Zhen Fung}
\position{Software Engineer{\enskip\cdotp\enskip}Data Scientist}
\address{847 Jurong West St 81 \#07-245 Singapore 640847}

\mobile{(+65) 97118507}
\email{chrisgzf@gmail.com}
%\homepage{www.posquit0.com}
\github{chrisgzf}
\linkedin{chrisgzf}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Human Resource Team}
  {Rohde \& Schwarz Asia Pte Ltd\\9 Changi Business Park Vista, \#03-01\\Singapore 486041}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{SgIS Scholarship Application - Rohde \& Schwarz}
% How the letter is opened
\letteropening{Dear Sir/Mdm,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Christopher Goh~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am a soon-to-be Computer Science undergraduate. My speciality is in artificial intelligence and data science, well-versed in implementing deep-learning neural networks. I was a founding member \& Director of Programmes of a non-profit society that organised tech workshops, competitions and hackathons for students and the disadvantaged. During my compulsory military service, I spearheaded leadership development projects in the Army. Contextualising the knowledge I have gained about military leadership to the private sector and coupled with my prior leadership experiences, I am suitably equipped with the skills required to build \& lead high-performing teams.

\lettersection{Why Rohde \& Schwarz?}
Purpose-driven, I enjoy work that make a difference in people's lives. Naturally, that has led me to my specialisation in AI, as I firmly believe that the digital world of tomorrow will be largely enabled by AI, where products \& services of higher quality \& complexity are created to enhance safety and the quality of people's lives. With Rohde \& Schwarz's wide diversity of solutions in many business fields, I feel like there is much scope for me to apply my skills to bring meaningful projects to fruition. Particularly, fields like wireless communications, signal processing, cybersecurity, are on the brink of an AI revolution --- recent advances in AI has allowed for novel applications in these fields, markedly improving performance --- and that excites me.

\lettersection{Why Me?}

Today, we live in a world shaken up by technological disruption, where trends \& threats have become increasingly volatile and uncertain. To thrive in such a turbulent world, one needs to be a fast learner, and a critical-thinker with mental tenacity. As a leader, one needs to be adaptive, well-informed of future developments to maintain strategic foresight, and be people-oriented as well to elevate the commitment and professional knowledge of those around him. Highly driven and inventive, coupled with my technical and leadership expertise, I feel like I am uniquely equipped with the traits mentioned above to be able to steer our organisation towards success in today's age of digital transformation.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
