%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Project Clerk, Leadership Branch, HQ Training \& Doctrine Command (Conscript)} % Job title
    {Singapore Army} % Organization
    {Singapore} % Location
    {Mar. 2017 - Jan. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Awarded the 2018 Army Full-time National Serviceman of the Year Award, Commander TRADOC Coin, Commander ALTI Letter of Appreciation, Commanding Officer 1st Commando Battalion Coin, Platoon Best Recruit.}
        \item {Produced LEARNet Video Courseware used for training Junior Commanders to lead their men more effectively.}
        \item {Organised Ops Staff Admin Course, Battalion Command Course, and Brigade-Level Command Course.}
        \item {Organised formation anniversary event as Head of Logistics and Chairman in 2017 and 2018 respectively.}
        \item {Conceptualised the Leader Strong Campaign – an initiative to streamline leadership development efforts across the Army to be focused on bridging its leadership gaps.}
        \item {Featured in Army Workplan Video 2018, under the Soldier Strong theme.}
        \item {Attended the Presidential Garden Reception 2018 @ Istana.}
        \item {Motivational Speaker for new SAF recruits at BMTC School V.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Part-Time Research Student (Artificial Intelligence)} % Job title
    {DSO National Laboratories} % Organization
    {Singapore} % Location
    {Jul. 2015 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a tool which made use of Natural Language Processing techniques to sift out key features of given input documents, fetch highly-related documents, and perform visualisation on accured data for Counter-Terrorism Profiling \& Disaster Monitoring, under the mentorship of Dr Terence Tan from DSO National Laboratories.}
        \item {Awarded a Bronze award at the Singapore Science \& Engineering Fair 2016.}
%.    \item {Shortlisted for the A*STAR Talent Search 2016.}
        \item {Presented and published research paper “Context Aware Web-mining Engine” in the IRC-SET Conference 2016.}
        \item {Presented to Assistant Director, Department Head, Program Director, Lab Head at DSO National Laboratories, and at YDSP Congress 2016.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Part-Time Research Student (Cognitive Science / Software Engineering)} % Job title
    {Nanyang Technological University} % Organization
    {Singapore} % Location
    {May. 2015 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Attached to School of Humanities and Social Sciences, Nanyang Technological University, mentored by Asst Prof Luca Onnis, under the Nanyang Research Programme.}
        \item {Created a front-end browser-based JavaScript game to measure human reaction times in cognitive tasks, backend NodeJS server to handle data collection, and analysed collected data with R.}
        \item {Received a Silver Award at the NRP Symposium 2016 for research paper "Creating Online Computer Games for Cognitive Training".}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Part-Time Research Student (Cryptography)} % Job title
    {DSO National Laboratories} % Organization
    {Singapore} % Location
    {Jul. 2014 - Apr. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a tool which cryptanalysed the Crypto1 cipher, and explored different factors which could affect the speed of algebraic cryptanalysis, under the mentorship of Ms Valerie Choy from DSO National Laboratories.}
        \item {Finalist at the Singapore Science \& Engineering Fair 2015.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
