%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Club President} % Affiliation/role
    {River Valley High School - Infocomm Club} % Organization/group
    {Singapore} % Location
    {2010 - 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Led a club of over 40 members in robotics, programming and multimedia education and competitions.}
        \item {Club clinched multiple consecutive national championships at the National Junior Robotics Competition, and represented Singapore in several international tournaments during the term.}
        \item {Organised robotics competitions to develop technical literacy and interest in primary and secondary school students.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Core Member \& Director of Programmes} % Affiliation/role
    {Gen-R} % Organization/group
    {Singapore} % Location
    {Jan. 2014 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Founded non-profit society with a few like-minded friends to develop youths in leadership, volunteerism and philanthropy through community outreach programs, and to increase IT literacy in the community.}
        \item {Organise tech-related competitions / workshops / hackathons for primary, secondary, tertiary students, and charity organisations. Events we organise include the Singapore Tech Challenge, Singapore Makers' Challenge, Robotics Workshop for members of SPD Singapore (previously 'Society for the Physically Disabled').}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Head of Publicity - Boon Lay Countdown 2015 \& 2016} % Affiliation/role
    {Boon Lay Community Centre} % Organization/group
    {Singapore} % Location
    {Oct. 2014 - Jan. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Worked with Grassroots leaders in organising the annual heartland new year countdown event, attended by over 30000 Boon Lay residents.}
        \item {Led a team of 10 in designing of all marketing collaterals and multimedia showcases.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Vice-Chairperson of Publications Committee} % Affiliation/role
    {River Valley High School - Y.LEAD Seminar 2015} % Organization/group
    {Singapore} % Location
    {Jan. 2015 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Led 20 members in the publicity operations of a week-long international youth leaders summit.}
        \item {In charge of setting up WordPress CMS functionality for event.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {River Valley High School - Science Leaders' Academy} % Organization/group
    {Singapore} % Location
    {2014 - 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Completed and presented 3 research projects at science conferences, competitions, and at a school exchange at Hackensack, NJ, USA.}
        \item {Organised science enrichment camps for primary school students to inculcate scientific interest and curiosity in them.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
